\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}

### 2021-01-15 papers/intro_paper/intro_paper.tex
changes in Sec. III

\subsection{Waveform model}\label{sec:model}

@@

\section{Results}\label{sec:results}

\subsection{\ab{Synthetic-signal injections in General Relativity with Gaussian noise}}\label{ssec:gr_signal}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for Injections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
 \hline
 Event & $m_{1,d} (\Mo)$ &  $m_{2,d} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
 \hline
 GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
 GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
 SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
 \hline
\end{tabular}
\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in teh first column. The parameters 
$(m_{1,d},m_{2,d})$ are the detector-frame masses of the primary and secondary BHs, respectively.}
\label{tab:injection_values}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\comment{AB: Nothing is said in the text about the third mock signal in the Table!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbt]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. \comment{AB: I would use a different color for the bottom figures, e.g., ``green''. Please also indicate on the figures: 
GW150914-like and GW190521-like.}}
	\label{fig:simulated_signal_GR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Simulations using modified GR signals in Gaussian noise}

To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger, and differ in their post-merger description. We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost done}. In other words, we assume that the frequency and damping time of our non-GR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}). We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. The posterior probability distributions on $(\df{220}, \dtau{220})$ or equivalently $(\fngr{220}, \taungr{220})$ (Fig.~\ref{simulated_signal_nonGR}) are consistent with the corresponding the values of the injection parameters, indicated by the black solid lines.

We additionally investigate the effects of erroneously assuming that an underlying modified GR signal can be well-described using GR. We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$. In such cases, we run the risk of biased parameter estimates due to an incomplete understanding of the underlying signal. The resulting posterior probability distributions are shown in the right panels of Fig.~\ref{simulated_signal_nonGR} by the pink (GW150914) and grey (GW190521) curves. The results are interesting and distinctly different for the two events. For the GW150914-like modified GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (Fig.~\ref{simulated_signal_nonGR} top right panel) are consistent with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no deviations (Fig.~\ref{simulated_signal_GR} top right panel). In other words, if the actual signal had deviations as large as the 50 \% of the GR prediction, the analysis with $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction. However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parameterized estimates: with and without deviations. The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise. A more detailed comparison of the other parameters, like the masses and spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR signal is shown in Fig.~\ref{fig:gr_ngr_comparison}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$. Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal.}
	\label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: non-GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for modGR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The underlying signal has a deviation, $\df{220} = \dtau{220} = XX$. The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. In the right panels, we additionally show measurements using a GR ($SEOB$) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased.}
	\label{fig:simulated_signal_nonGR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Test of the No hair theorem}\label{ssec:nohairtheorem}

@@

\subsection{Results on actual LIGO-Virgo results}

>>>>

\ab{\subsection{Parameterized waveform model}}\label{sec:model}

@@

\section{Synthetic-signal injection study}\label{sec:results}

\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for Injections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
 \hline
 Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
 \hline
 GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
 GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
 SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
 \hline
\end{tabular}
\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively. \comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages. The third row is completely ignored in the caption's explanations.}}
\label{tab:injection_values}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbt]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. \comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
	\label{fig:simulated_signal_GR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}

To demonstrate the robustness of the method in detecting possible
deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
the corresponding GR prediction up to merger, and differ in their post-merger
description. We again choose \sout{systems with initial-}binary-parameters
similar to GW150914 and GW190521 (as given in Table XXX), but 
\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
\ab{set} $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost
  done}. In other words, we assume that the frequency and damping time
of our non-GR signal is 1.5 times the corresponding GR prediction,
although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
you just clearly refer to thePlease introduce the injected signal and the template, which is used 
to recover it, and simply say that they belong to the same waweform model.} 
We also avoid waveform \sout{and noise} systematic biases by choosing 
a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
explaining the results in teh figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}

We additionally investigate the effects of erroneously assuming that
\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
signals using the GR waveform model $\SEOB$ instead of the parameterized 
$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
In such cases, we run the risk of biased parameter estimates due to an
incomplete understanding of the underlying signal. The resulting
posterior probability distributions are shown in the right panels of
Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
(GW190521-like) curves.} The results are interesting and distinctly
different for the two events. For the GW150914-like \comment{AB: I would avoid using 
``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
reported \emph{no} deviation from the GR prediction. However in the
case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
the non-GR signal would have yielded measurements distinctly
different from either of the two parameterized estimates: with and
without deviations. \comment{AB: Not clear to me the next sentence. We are working 
in Gaussian noise, so why are you referring to the noise as the culprit or the 
source of difference?} The fact that the GW190521-like signal has a much
lower SNR than GW150914-like signal might be a possible reason for the 
measurement of the final quantities to be more susceptible to noise. A
more detailed comparison of the other parameters, like the masses and
spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR
signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
comment the figures. What are the main results? What do we deduce?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$. Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal. \comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from teh y-axis labels, but instead provide 
explanations in the caption, and use only $f(t)$.}}
	\label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: non-GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for modGR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The underlying signal has a deviation, $\df{220} = \dtau{220} = XX$. The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. In the right panels, we additionally show measurements using a GR (\SEOB) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased. \comment{AB:The labels of the plots on theright are 
wrong, I believe, because otehrwise I don't understand the results. Please rewrite the caption in a more concise and clear way. It is difficult 
to understand it. We are not using the notation ``modGR'' anywhere else in the paper. We don't invent new notations each time!}}
	\label{fig:simulated_signal_nonGR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}

@@

\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
